Transforming Trash as an Artistic Act

### 2015-12-06 chapter3_reduced.tex
reduction, new images, artworks
Former-commit-id: c40034851af5d836cbdf7de2f0d9443a70979999

%
%
\section{Root in the Art History}
Using trashed objects in making of art can be examined with the enterance of non-art objects to art \todo{sadece bu yeterli olmayabilir.}. In other words using objects in artworks beyond their intended purpose or intended meaning and function. Developing artworks not only painting but also using paper and other stuff by pasting (or putting) them together. (How using non-art objects affected art?) \comment{Using object apart from their proposed meaning is not a new thing, through the ages people used objects and tools for different purposes. However it is not discussed in the context of fine art and not accepted method for art making.} First one is a collage work of Picasso. \todo{Still Life with Chair Caning} \todo{Violin with sheet of music}. One of the earliest examples is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth with an imitation chair caning design was pasted onto the painting. This work of Picasso also can be considered as first example of assamblage because of a rope was used to frame the picture. Using non-art objects in the production of art challanges existing conventions of painting. 
% FROM http://www.sparknotes.com/biography/picasso/section7.rhtml
\paraphrase{This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas. The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.} \comment{\textbf{Pablo Picasso} first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).} \textbf{Marcel Duchamp} is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art. The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.

% FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
\todo{works of Kurt Schwitters} \paraphrase{The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay. \ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality. Material has transformed into information, and ‘how’ has surpassed ‘what’ we see. The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.}

% TODO paraphrase
\quotes{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters. Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano. Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H. A. Schuldt’s famous “Trash People,” which has traveled around the world since 1996}  \cite{tauxe2012encyclopedia}.

%
%
[Collage] Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or found materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting. In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions. Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}. \todo{read greenberg1984collage}

%
%
[Assemblage] Assemblage work produced by the incorporation of everyday objects into a composition. It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional. Diverse range of things can be used production of work. In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art. William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}. \todo{Joseph Cornell, assemblage artist.}

%
%
[Bricolage] Dictionary meaning\todo{which dictionary}; something constructed using whatever was available at the time. \paraphrase{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available. It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old. \cite{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}

\paraphrase{\ldots someone that creates bricolage is described as a \quotes{bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends}.}

\begin{quote}
[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project. His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
\end{quote}

\begin{quote}
The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth. There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
\end{quote}

\begin{quote}
The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon. In this sense the engineer is a myth. A subject who would supposedly be the absolute origin of his own discourse and would supposedly construct it 'out of nothing,' 'out of whole cloth,' would be the center of the verbe, the verbe itself. The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
\end{quote}

[TODO use this ref]\cite{strasser1999waste}

%
%
[Found Object] Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.

%
%
[Ready-Mades]

@@

% FROM ReVista
\todo{başka bir yerde kullan. Trash is dirty. Trash is smelly.} \paraphrase{Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}

@@

%
%
\textbf{Sad Chair.} can be add here. Very similar to road kill, captures the record of city life. Leaved alone chairs somewhere in the city.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
  \caption{Pictures of Garbage by Vic Muniz}
  \label{fig:VicMuniz_PicturesOfGarbage}
\end{figure}

@@

@@

\todo{indiginazation of western goods here.}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[height=6cm]{graphics/Alsbrooks.jpg}
  \caption{The White Trash Series by Kim Alsbrooks}
  \label{fig:Alsbrooks}
\end{figure}

@@

\textbf{Martin Kaltwasser \& Folke Föbberling: City As a Resource.} One Man's Trash Is Another Man's Treasure. Garbage dump or gold mine? The German artistic collaborators Martin Kaltwasser and Folke Köbberling see rubbish as a major resource. Their projects colonize public space in the name of recycling and design: Overnight, they can make pavilions, villages of huts and even whole houses appear. In installations, exhibitions and, most frequently, guerrilla architectural interventions, they question the conditions of urban life as determined by privatization. For example, in a 2004 project called "Hausbau," they built a house in front of West Berlin's infamous Gropius-designed, failed-utopia high-rise development, Gropiustadt, and moved their family into it for a one week stay; for 2005's "Kleinod," they built a bridge and a stairway between a local family's home and a nearby community garden. In City as a Resource: One Man's Trash Is Another Man's Treasure, Köbberling and Kaltwasser propose simple ways of livening up and re-appropriating the urban habitat with sly alternatives to conventional urban planning.

Dump or rich source – the "free materials" discovered on the street, on wasteland and on building site rubbish dumps and recycled by Martin Kaltwasser and Folke Köbberling experience incredible metamorphoses. Pavilions, villages of huts and even whole houses are appearing over night. Since 2002 the artists have been using public space as their field of experiment in projects on the use of (free) resources. In installations, exhibitions and most frequently, in actual interventions they question the conditions of urban life determined by privatisation and economisation. Through realised projects the book reveals simple ways of livening up and re-appropriating the City as a Resource and thus offers new components in an alternative to conventional urban planning. Köbberling and Kaltwasser propose informal and self-organised structures rather than the usual methods emphasising control, security and as much marketing as possible. Their approach demonstrates that often – with the help of their own clever building logistics – a huge impact may be made with a minimum of financing.

% From Hold it! : the art & architecture of public-space-bricolage-resistance-resources-aesthetics of Folke Köbberling and Martin Kaltwasser
Public space is under siege. The compulsion to consume, increased monitoring, and continuous traffic expansion will bring fundamental change to the appearance of cities. In 1998, Folke Kobberling and Martin Kaltwasser began implementing their concept of an artistic and architectural aesthetic of resistance to this appropriation. Using 'structural interventions' in streets, squares, bridges, parks and interior spaces they propose alternatives formed of urban 'waste': litter, trash, and other discarded or donated material.

Köbberling\&Kaltwasser’s large architectural structures attempt to make visible the value of movement and communication through the transformation of found materials into publicly used objects and spaces. Using the city as a field of artistic experimentation, addressing issues of public space and sustainability, their installations, exhibitions and interventions critically question privatisation and economic pressures. The work will be an act of resistance to occupy and reclaim a space and change its meaning. At the same time, the work mirrors the socio-economic aspect of the city - the city as a resource, the materiality of the city, the free material of a city.

For their projects they use the “city as a resource” and draw on materials they find in urban spaces, for example in containers or on building sites.

Public space and transformed materials.

% From: http://www.goethe.de/ins/cz/prj/art/kue/koe/enindex.htm
Public space is under siege: pressure to consume, growing control and more and more traffic are threatening to change the picture of our cities dramatically. The couple Folke Köbberling and Martin Kaltwasser have been elaborating their idea of an artistic and architectonical aesthetics of resistance against this take-over since 1998.

They confront consumerist ideologies with alternatives: structural intervention, artistic statements, actions and theories. In doing so, the artists make use of streets, squares, bridges, parks and interiors as operational spaces. And the material they use is always obtained from urban resources: things that have been thrown away, garbage, donated things.

>>>>

%
%
\section{Root in the Art History}
Using trashed objects in making of art can be examined with the enterance of non-art objects to art\todo{sadece bu yeterli olmayabilir}. In other words, using objects in artworks beyond their intended purpose or intended meaning and function. Developing artworks not only painting but also using paper and other stuff by pasting (or putting) them together. (How using non-art objects affected art?) \comment{Using object apart from their proposed meaning is not a new thing, through the ages people used objects and tools for different purposes. However it is not discussed in the context of fine art and not accepted method for art making.} First one is a collage work of Picasso. One of the earliest examples is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth with an imitation chair caning design was pasted onto the painting. This work of Picasso also can be considered as first example of assemblage because of a rope was used to frame the picture. Using non-art objects in the production of art challenges existing conventions of painting. 
% FROM http://www.sparknotes.com/biography/picasso/section7.rhtml
\paraphrase{This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas. The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.} \comment{\textbf{Pablo Picasso} first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).}

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/picasso_chair.png}
  \caption{Pablo Picasso, Still Life with Chair Caning, 1912, oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
  \label{fig:Picasso_Chair}
\end{figure}

\textbf{Marcel Duchamp} is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art. The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
  \caption{Marcel Duchamp, Bicycle Wheel, 1913 (authorised reproduction 1951, original lost)}
  \label{fig:Duchamp_BicycleWheel}
\end{figure}

% FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
\todo{works of Kurt Schwitters} \paraphrase{The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay. \ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. As he wrote: ‘It grows more or less according to the principle of a metropolis.’ The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality. Material has transformed into information, and ‘how’ has surpassed ‘what’ we see. The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.}

% TODO paraphrase
\paraphrase{The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters. Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano. Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H. A. Schuldt’s famous “Trash People,” which has traveled around the world since 1996 \cite{tauxe2012encyclopedia}.}

%
%
\summary{Collage}
Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or found materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting. In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions. Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}. \todo{read greenberg1984collage}

% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\summary{Hybridity} 
\paraphrase{Recycled object contains within it a reference to two or more distinct times. Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992)} \todo{ref.}

% TODO MOVE
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%\comment{Different meanings for everybody.} 
%\paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaning for another. Different objects have different life spans --- different degrees of permanence or disposability --- and that these life spans are socially constituted is also an integrated part of the story \ldots geographic and socioeconomic boundaries of class, caste and culture throughout the world. It is story of people --- the women, men, children etc. one person's trash into another's treasure.}

% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap 
It is claimed that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} \paraphrase{Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple technologies, histories and temporalities.}

% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
\paraphrase{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence. Recycling always implies a stance toward time --- between the past and the present --- and often a perspective on cultures --- one's own and others. (Jacknis 1992)} \todo{ref.}

% TODO MOVE TO COMMON APPROACH
%\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}

%
%
\summary{Assemblage} 
Assemblage work produced by the incorporation of everyday objects into a composition. It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional. Diverse range of things can be used production of work. In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art. William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}. \todo{Joseph Cornell, assemblage artist.}

%
%
\summary{Bricolage} 
Dictionary meaning\todo{which dictionary}; something constructed using whatever was available at the time. \paraphrase{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available. It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old. \cite{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}

\paraphrase{\ldots someone that creates bricolage is described as a bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends.}

%\begin{quote}
%[He or she] is adept at performing a large number of diverse tasks; but, unlike the engineer, he [or she] does not subordinate each of them to the availability of raw materials and tools conceived and procured for the purpose of the project. His [or her] universe of instruments is closed and the rules of his [or her] game are always to make do with “whatever is at hand,” that is to say with a set of tools and materials which is always finite and is also heterogeneous because what it contains bears no relation to the current project, or indeed to any particular project, but is the contingent result of all the occasions there have been to renew or enrich the stock or to maintain it with the remains of previous constructions or destructions.\cite{levi1966savage}
%\end{quote}

%\begin{quote}
%The bricoleur, says Levi-Strauss, is someone who uses 'the means at hand,' that is, the instruments he finds at his disposition around him, those which are already there, which had not been especially conceived with an eye to the operation for which they are to be used and to which one tries by trial and error to adapt them, not hesitating to change them whenever it appears necessary, or to try several of them at once, even if their form and their origin are heterogenous---and so forth. There is therefore a critique of language in the form of bricolage, and it has even been said that bricolage is critical language itself\ldots If one calls bricolage the necessity of borrowing one's concepts from the text of a heritage which is more or less coherent or ruined, it must be said that every discourse is bricoleur.\cite{derrida1993structure}
%\end{quote}

%\begin{quote}
%The engineer, whom Lévi-Strauss opposes to the bricoleur, should be the one to construct the totality of his language, syntax, and lexicon. In this sense the engineer is a myth. A subject who would supposedly be the absolute origin of his own discourse and would supposedly construct it 'out of nothing,' 'out of whole cloth,' would be the center of the verbe, the verbe itself. The notion of the engineer who had supposedly broken with all forms of bricolage is therefore a theological idea; and since Lévi-Strauss tells us elsewhere that bricolage is mythopoetic, the odds are that the engineer is a myth produced by the bricoleur.\cite{derrida1993structure}
%\end{quote}

%[TODO use this ref]\cite{strasser1999waste}

%
%
\summary{Found Object} 
Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%\comment{GIFT FROM GOD, NOT KNOWING PREVIOUS STATE} They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors). From western trash to tribal treasure. \paraphrase{For the Kalahari Bushmen, the process appears to be one not so much of reusing but of creating anew; not so much transforming, a inventing (p.9).} It stated these found objects is accepted as a gift from gods. A disposable item becomes imminent desire and profound social consequence. (Intercultural recycling.) \paraphrase{Both presentations tell a story about an aesthetic and cross-cultural process --- as well as an economic and political one --- which is defined by the act of recovering and transforming the detritus of the industrial age into handmade objects of renewed meaning, utility, devotion, and sometimes arresting beauty (p.10).}

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%[Having different meanings] For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function. It is case from the film and also the case depicted in the real life photographs taken by anthropologist michael leahy which document his first colonial contact with new guinean highlanders.

% TODO new comer
% Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%\todo{yerlinin fotoğrafı}
%\quotes{Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head. In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.} \todo{ref.}

%(Summary From Paul M Camic.) 
%The term found object, as used in this article, refers to an existing object or artifact that is picked up (found) and generally not bought or originally intended as art, yet it is also considered to have some value (e.g., aesthetic, novelty, remembrance) to the finder. It is during the locating and finding process that the value of the object, once considered to be junk or rubbish, changes. The junk object becomes transformed into the valued found object. Objet trouve, translated from the French as “object found,” appears to have been first used by Marcel Duchamp in 1913 in reference to objects he made use of in his “readymade” art (Richter, 1965). His earliest known application for an objet trouve was seen in his well-known piece Bicycle Wheel, “where he had simply upturned a wheel on a stool” (Gale, 1997, p. 97) and labeled it a work of art. A more public and controversial introduction of the readymade occurred in 1917 when Duchamp attempted but failed to exhibit the highly contentious piece The Fountain, where a single white urinal became a readymade piece of art (Tomkins, 1996). These pieces were the beginning of Duchamp’s shift from an art striving for beauty and possessing a higher complex or hidden meaning beyond what was seen to an art form that made use of, and occasionally celebrated, the common materials and objects found in everyday living.

%Gascoygne (1936), writing about the artist’s use of “the strange medley of materials” (p. 169), referred to as objets trouve in Surrealist art, suggesting that the artist “discovers a hidden symbolic significance in the [found] object which is preserved when the object is ‘framed’ as art” (p. 170). The finder discovers an unrealised significance in the object. A new boundary is formed around the object by the finder through removing it from its found environment and placing it in a new one, thus empowering the finder in the role of creating a new reality for the object. He argued that the found object, before it is found, approximates a zero value aesthetically; the zero value increases for the finder---beholder on discovery of the object and increases further if the object is placed in another context. \ldots the meaning of material objects was derived from their symbolic relation to another (e.g., person, time, place, experience) rather than through their physical attributes (Causey, 2003; Csikszentmihalyi \& Rochberg-Halton, 1981).

%How a region of flexibility develops, what social factors are involved in taking innovative and creative responses toward rubbish, and how an individual changes (and enhances) his or her creative responses toward society’s detritus are areas that require additional examination. (Important points a gap in the literature. Although Parsons article analyze practices, it is not very broad and detailed. Further what is the importance of it is missing.)

%The importance and enjoyment of found objects to those who participated in this study, using them in various ways and for different reasons, were strongly evident. The interaction between finder and object is an attempt to make meaning of an object that has been found, and by being found and desired becomes transformed.

%Gascoygne (1936) recognized that finding an unrealized significance in a material (found) object was empowering partially because, through the creative agency of the finder, the object’s aesthetic value had increased from zero to something greater. The transformation of rubbish from a negative value to a positive value requires the finder to develop a symbolic meaning, and sometimes a functional use, for the object that goes beyond its present situation as culturally labeled detritus while simultaneously responding to its current physical and aesthetic elements. When the found object is seen by the finder as a symbol representing another entity (e.g., when an old blue bottle with foreign lettering comes to symbolize far away intrigue, mystery, and sophistication), support is given to what Dittmar (1992) described as socially constructing a material identity for the object. Expanding on Dittmar’s use of a social interactionist perspective, the results of the present study support the possibility that the entire found object process---finding, reclassifying, and reusing objects---becomes a symbol of identity for the finder. This supports Digby’s (2006) argument that individuals make use of salvaged objects as souvenirs, which are no longer part of the commodity cycle, to rework and construct individual and social identities.

%An important difference, however, which also appears to contribute to the aesthetic experience, takes place when discovering an object unexpectedly in a nonpredetermined place and time. Unlike appreciating art in a museum, which is a boundaried activity occurring at a scheduled time and place with the anticipation of finding and looking at art objects, finding discarded objects can occur anywhere at anytime and thus, according to participants, can “trigger” a burst of sensory attention and a “surge” of cognitive activity on the part of the finder.

%Results of this study also support consideration of found objects as important artifacts that are signifier of cultural meaning.

% [TODO adapt for my case] Found objects first came to the attention of the general public through their use by artists in early part of the 20th century. To help contextualize the application of found objects, the following section provides an overview of their use by Western artists. This is followed by an examination of objects in human development and includes aspects of psychoanalytic theory, material objects and their relationship to identity, selected cognitive theories, and an outline of the social life of objects through rubbish theory.

% Amelie olabilir. Orada fotoğraf toplayan çocuk olabilir. Onları itinayla toplayan bir adam. Tren garındaki fotoğraf kulubesi. Belki de dünyanın dört bir yanından gelen insanlar, bir kesişim noktası. Bir birinden farklı bir sürü insan. Filmde neden böyle bir eyleme yer veriliyor? Film fotoğraflar üzerinden defter üzerinden ilerliyor. Onun çevresinden bir hikaye kurgulanıyor. İnsanların artıklarını topluyor. Onların değer vermedikleri şeyleri topluyor. Bunlar baya baya aslında o insanlar. Bazı fotoğraflar çok fazla küçük parçalara ayrılıyor. Çok iyi bir örnek mi bilmiyorum. Burada niyet nedir ki? Ben buna şöyle bir okuma getireceğim diyebilirim. Amelie mesela küçük ayrıntılara dikkat eden bir insan, bu fotoğraf taplama işi de aynı şekilde. Bu arada bu fotoğraf toplama işi ilk değil. Found photos diye başka bir paper var ve orada aslında bu işin ilk uygulaması gösterilmekte. Ama benim işime yarayan kısmı ne? Neden o fotoğrafları ya da bunun filmini yapıyor. Aslında puzzlelar üretiyor. Belirli tekrar olacaktır. insanların kapalı bir ortamda nasıl pozlar verdiklerini sonrasında ise onları attıkları şeylerden görülebilir. Tekrar bir kitap haline geliyor. Tanınmayan insanların fotoğrafları. Nerde oldukları, neden ve nasıl çekildikleri belli olmayan bu yüzden aslında ilişkilerin insanlara bırakıldığı bir koleksiyon. Aslında tam da amelie bunu yapmıyor mu? Hikayeler üretiyor bu fotoğraflardan. Yeni karşılaşmalar üretmesi. Her ne kadar sıradan portre fotoğraflar olsa da birbirlerinden oldukça farklılardır. Bin bir türlü şey vardır aralarında. Nereye yerleşmeli. Başkasının çöpünü toplama. O dönemin o eşyasını arşivini tutma. ve herkes sunuluyor sonrasında bu.

%
%
%[Ready-Mades]

@@

% not easily understandable with the entering non-art objects in art. artist are responding the current societies habits in a different ways. what they are doing here is to see other possibilities and show actually what is going on. what does it mean all of these things.

% FROM ReVista
%\todo{başka bir yerde kullan. Trash is dirty. Trash is smelly.} 
\paraphrase{Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}

@@

%
%
%\textbf{Sad Chair.} can be add here. Very similar to road kill, captures the record of city life. Leaved alone chairs somewhere in the city.

@@

\begin{wrapfigure}{r}{0.4\textwidth}
  \begin{center}
    \includegraphics[width=0.37\textwidth]{graphics/vik-muniz-picturesofgarbage0.jpg}
  \end{center}
  \caption{Vic Muniz, Pictures of Garbage}
  \label{fig:VicMuniz_PicturesOfGarbage}
\end{wrapfigure}

@@

\comment{This is a proff of the transformation of the original concept.}

% TODO new comer.
[Reasons of recycling] \comment{Economic conditions forces to people recycle and reuse. but even if they have no economical struggle, they continue recycle. what is the reason of it?} Recycling as an economic strategy of survival in developing countries throughout the world. creative production that is motivated, primarily, by adverse conditions of economic necessity. (lanfill orchestra here. bookcovers here.) Economic survival and adaptation are influential factors for both the makers, who build informal business on the making and selling of recycled goods, and the local consumers, for whom the market for affordable, utilitarian goods is devised. (p25)

@@

\summary{Indigenization} 
The indigenization of western objects. (sahlins, 16) Do these hybrid objects, as many western critics might assume, point to passive acceptance of a homogenized consumer culture in the service of western capitalist expansion, or, even worse, a sense of want and deprivation when confronted with "our riches"? Marshall Sahlins: "The first commercial impulse of the local people is not to become just like us, but more like themselves. They do not necessarily despise our commodities. But they are selective in their demands and transformative of their uses of such things. (sahlins, 13)"

@@

\begin{wrapfigure}{r}{0.4\textwidth}
  \begin{center}
    \includegraphics[width=0.37\textwidth]{graphics/Alsbrooks.jpg}
  \end{center}
  \caption{Kim Alsbrooks, The White Trash Series}
  \label{fig:Alsbrooks}
\end{wrapfigure}

@@

[Chrish Jordan Break Down inventory] \paraphrase{Not all artist transform trash although some deconstruct them. Michael Landy is one of them. Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers. Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part. Reveal all his possessions. and loosing them while you are alive. Turning them to rubbish making them unusable. breaking down the all the meaning. breaking down the connections.} It can be an example of downcycling process. It is preferred to decompose all the complex link and relationships between the objects. They are not just ordinary things they are possessions of artist. Break Down 2001, in which he systematically destroyed all his personal possessions. His work examines what we value and what we discard, consumerism and waste, and human labour and its worth. It happens in public space. People can see the process. This process last 2 weeks. Places where people buy things actually.

%\comment{Tüm sahip olduklarını yaşarken kendi isteği ile yok ediyor. Bu hepimizin paylaştığı bir şey.}

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/ChrisJordan_BreakDown.jpg}
  \caption{Chris Jordan, Break Down}
  \label{fig:ChrisJordan_BreakDown}
\end{figure}

%\textbf{Martin Kaltwasser \& Folke Föbberling: City As a Resource.} One Man's Trash Is Another Man's Treasure. Garbage dump or gold mine? The German artistic collaborators Martin Kaltwasser and Folke Köbberling see rubbish as a major resource. Their projects colonize public space in the name of recycling and design: Overnight, they can make pavilions, villages of huts and even whole houses appear. In installations, exhibitions and, most frequently, guerrilla architectural interventions, they question the conditions of urban life as determined by privatization. For example, in a 2004 project called "Hausbau," they built a house in front of West Berlin's infamous Gropius-designed, failed-utopia high-rise development, Gropiustadt, and moved their family into it for a one week stay; for 2005's "Kleinod," they built a bridge and a stairway between a local family's home and a nearby community garden. In City as a Resource: One Man's Trash Is Another Man's Treasure, Köbberling and Kaltwasser propose simple ways of livening up and re-appropriating the urban habitat with sly alternatives to conventional urban planning.

%Dump or rich source – the "free materials" discovered on the street, on wasteland and on building site rubbish dumps and recycled by Martin Kaltwasser and Folke Köbberling experience incredible metamorphoses. Pavilions, villages of huts and even whole houses are appearing over night. Since 2002 the artists have been using public space as their field of experiment in projects on the use of (free) resources. In installations, exhibitions and most frequently, in actual interventions they question the conditions of urban life determined by privatisation and economisation. Through realised projects the book reveals simple ways of livening up and re-appropriating the City as a Resource and thus offers new components in an alternative to conventional urban planning. Köbberling and Kaltwasser propose informal and self-organised structures rather than the usual methods emphasising control, security and as much marketing as possible. Their approach demonstrates that often – with the help of their own clever building logistics – a huge impact may be made with a minimum of financing.

% From Hold it! : the art & architecture of public-space-bricolage-resistance-resources-aesthetics of Folke Köbberling and Martin Kaltwasser
%Public space is under siege. The compulsion to consume, increased monitoring, and continuous traffic expansion will bring fundamental change to the appearance of cities. In 1998, Folke Kobberling and Martin Kaltwasser began implementing their concept of an artistic and architectural aesthetic of resistance to this appropriation. Using 'structural interventions' in streets, squares, bridges, parks and interior spaces they propose alternatives formed of urban 'waste': litter, trash, and other discarded or donated material.

%Köbberling\&Kaltwasser’s large architectural structures attempt to make visible the value of movement and communication through the transformation of found materials into publicly used objects and spaces. Using the city as a field of artistic experimentation, addressing issues of public space and sustainability, their installations, exhibitions and interventions critically question privatisation and economic pressures. The work will be an act of resistance to occupy and reclaim a space and change its meaning. At the same time, the work mirrors the socio-economic aspect of the city - the city as a resource, the materiality of the city, the free material of a city.

%For their projects they use the “city as a resource” and draw on materials they find in urban spaces, for example in containers or on building sites.

%Public space and transformed materials.

% From: http://www.goethe.de/ins/cz/prj/art/kue/koe/enindex.htm
%Public space is under siege: pressure to consume, growing control and more and more traffic are threatening to change the picture of our cities dramatically. The couple Folke Köbberling and Martin Kaltwasser have been elaborating their idea of an artistic and architectonical aesthetics of resistance against this take-over since 1998.

%They confront consumerist ideologies with alternatives: structural intervention, artistic statements, actions and theories. In doing so, the artists make use of streets, squares, bridges, parks and interiors as operational spaces. And the material they use is always obtained from urban resources: things that have been thrown away, garbage, donated things.
